Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-04-28 sec_intro.tex
ok until we finalize the results and other sections

Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle. Of particular interest in studies of possible novel  collective effects is the long-range structure of two-particle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small. In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in $\Delta\eta-\Delta\phi$ plot.
The shape of these $\Delta\phi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}. The second and third order terms are the dominant harmonic coefficients $v_n$. The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.

@@

>>>>

@@

Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle. Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small. In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in $\Delta\eta-\Delta\phi$ plot.
The shape of these $\Delta\phi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}. The second and third order terms are the dominant harmonic coefficients $v_n$. The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
